### 2021-10-28 manuscript/hiv-gwas.tex
Update on Overleaf.

\begin{figure}
\includegraphics[width = 0.3\linewidth]{figures/spvl_on_tree.png}
	\caption{Inferred HIV-1 $pol$ gene phylogeny with tips colored by calculated spVL and estimated pathogen and non-pathogen parts of spVL.}
	\label{fig:spvl-on-tree}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width = 0.7\linewidth]{figures/spvl_on_tree.png}
	\caption{Inferred HIV-1 $pol$ gene phylogeny with tips colored by (A) calculated spVL, (B) estimated non-pathogen effects on spVL and (C) estimated pathogen effects on spVL.}
	\label{fig:spvl-on-tree}
	\end{center}
\end{figure}
